1-Step, 3-Factor Authentication with Custom-Fit, In-Ear EEG

### 2017-02-06 paper.tex
updated abstract

\maketitle
\begin{abstract}
In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all subjects, we achieve a best-case false acceptance, XX% false rejection rate with data from only one earpiece. In a preliminary test of an ``imposter'' spoof attack, we find a 0% false acceptance rate. _Conclusions and relevance_.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all subjects, we achieve a best-case XX\% false acceptance, XX\% false rejection rate with data from only one earpiece. In a preliminary test of an ``imposter'' spoof attack, we find a 0\% false acceptance rate. \underline{Conclusions and relevance}.
\end{abstract}
